msAggr_seurat

### 2021-11-08 IndividualPops/Individual_SubpopAnalyses.Rmd

## Set global variables
```{r}
pop.id <- "CMP"
folder.appendix <- "m2"
fav.var <- 90
object.res <- ".1"
ident.list <- c("RNA_snn_res.0.5", "RNA_snn_res.1")
folder.id <- paste0(pop.id, folder.appendix)
projectName <- paste0(pop.id, "Subpop")
```

@@

# ID clusters based on different variances
## Describe 80% of variance with 12 dimensions

@@

## DGE w/ object
Strt with comparing all clusters against all other clusters and write out cluster info
calculate `FindAllMarkers()` for different idents and save to new file
```{r}
# ident.list <- colnames(seurat.object@meta.data)[grepl("^RNA_snn", colnames(seurat.object@meta.data))]

@@

calculate `FindMarkers()` that distinguish each cluster (might overlab between clusters)
```{r}
# ident.list <- colnames(seurat.object@meta.data)[grepl("^RNA_snn", colnames(seurat.object@meta.data))]
ident.list <- c("RNA_snn_res.0.5", "RNA_snn_res.1")
for(tested.ident in ident.list){
	for (cluster in sort(as.numeric(levels(seurat.object@meta.data[[tested.ident]])))){
		cluster.markers <- FindMarkers(seurat.object, ident.1 = cluster)
		xlsx::write.xlsx(x = cluster.markers[,c("avg_log2FC", "p_val_adj")], 
										 file = paste0(projectName, "_FindMarkers_pctVar", pct.var, gsub("RNA_snn_", "", tested.ident), ".xlsx"), 
										 sheetName = paste0("clst", cluster), 
										 col.names = TRUE, 
										 row.names = TRUE, 
										 append = TRUE)
	}
}
```

>>>>

## Set global variables
```{r}
pop.id <- "CMP"
folder.appendix <- "m2"
fav.var <- 90
pct.var <- 90
object.res <- ".1"
ident.list <- c("RNA_snn_res.0.5", "RNA_snn_res.1")
folder.id <- paste0(pop.id, folder.appendix)
projectName <- paste0(pop.id, "Subpop")
```

@@

# ID clusters based on different variances
## Describe 80% of variance

@@

## DGE w/ object
Strt with comparing all clusters against all other clusters and write out cluster info
calculate `FindAllMarkers()` for different idents and save to new file  
### [Note from devs](https://www.biostars.org/p/409790/):
"FindMarkers will find markers between two different identity groups - you have to specify both identity groups. This is useful for comparing the differences between two specific groups.

FindAllMarkers will find markers differentially expressed in each identity group by comparing it to all of the others - you don't have to manually define anything. Note that markers may bleed over between closely-related groups - they are not forced to be specific to only one group. This is what most people use (and likely what you want).

FindConservedMarkers will find markers that are conserved between two groups - this can be useful if you want to find markers that are conserved between a treated and untreated condition for a specific cell type or group of cells. It means they are differentially expressed compared to other groups, but have similar expression between the two groups you're actually comparing."
```{r}
# ident.list <- colnames(seurat.object@meta.data)[grepl("^RNA_snn", colnames(seurat.object@meta.data))]

@@

calculate `FindMarkers()` that distinguish each cluster 
```{r}
# ident.list <- colnames(seurat.object@meta.data)[grepl("^RNA_snn", colnames(seurat.object@meta.data))]
ident.list <- c("RNA_snn_res.0.5", "RNA_snn_res.1")
for(tested.ident in ident.list){
	for (cluster in sort(as.numeric(levels(seurat.object@meta.data[[tested.ident]])))){
		cluster.markers <- FindMarkers(seurat.object, ident.1 = cluster)
		xlsx::write.xlsx(x = cluster.markers[,c("avg_log2FC", "p_val_adj")], 
										 file = paste0(projectName, "_FindMarkers_pctVar", pct.var, gsub("RNA_snn_", "", tested.ident), ".xlsx"), 
										 sheetName = paste0("clst", cluster), 
										 col.names = TRUE, 
										 row.names = TRUE, 
										 append = TRUE)
	}
}
```

### 2021-11-08 msAggr_seurat/msAggr_seurat.Rmd

```{r}
for (meta.col in colnames(seurat.object@meta.data)){
	if(grepl(pattern = "RNA_snn_res", x = meta.col)==TRUE | grepl(pattern = "orig.ident", x = meta.col)==TRUE){
		myplot <- DimPlot(seurat.object, 
											group.by = meta.col,
											reduction = "umap", 
											pt.size = 1,
											cols = color.palette) + 
			ggtitle(paste0(projectName, " dim", ndims, "res.", gsub("RNA_snn_res.", "", meta.col) ))
		plot(myplot)
		png(filename = paste0(projectName, " dim", ndims, "res.", gsub("RNA_snn_res.", "", meta.col), "-umap.png"), height = 800, width = 800)
		plot(myplot)
		dev.off()
		myplot <- DimPlot(seurat.object, 
											group.by = meta.col,
											reduction = "umap", 
											pt.size = 1,
											cols = color.palette) + 
			facet_wrap(meta.col) + 
			ggtitle(paste0(projectName, "dim", ndims, "res.", gsub("RNA_snn_res.", "", meta.col)))

		png(filename = paste0(projectName, "dim", ndims, "res.", gsub("RNA_snn_res.", "", meta.col), "-umap_FacetRes.png"), height = 800, width = 800)
		plot(myplot)
		dev.off()

	}
}
```
Plot gene expression
```{r}
feature.list <- c("Meis1", "Gata2", "Gata1", "Irf8", "Elane", "Fli1", "Zfpm1")

@@

## DGE w/ resolution = 0.5
Strt with comparing all clusters against all other clusters and write out cluster info
calculate `FindAllMarkers()` for different idents and save to new file
```{r}
# ident.list <- colnames(seurat.object@meta.data)[grepl("^RNA_snn", colnames(seurat.object@meta.data))]
ident.list <- c("RNA_snn_res.0.5", "RNA_snn_res.1")

@@

	## Map HGNC symbols
	Mouse2HumanTable <- Mouse2Human(all.markers$gene)

	HGNC <- with(Mouse2HumanTable, Mouse2HumanTable$HGNC[match(all.markers$gene, Mouse2HumanTable$MGI)])
	all.markers$HGNC <- HGNC
	sig.res <- all.markers[all.markers$p_val_adj <= 0.05, ]
	sig.res <- sig.res[c("avg_log2FC", "HGNC", "cluster")]
	sig.res <- sig.res[!(sig.res$HGNC == "" | is.na(sig.res$HGNC)),] # GSEA will fail if there are any blanks or NAs in the table
	sig.res <- sig.res[]

	for(cluster in unique(sig.res$cluster)){
		print(paste("writing cluster", cluster))
		new.table <- sig.res[sig.res$cluster == cluster, c("HGNC", "avg_log2FC")]
		new.table <- new.table[order(-new.table$avg_log2FC), ]
		try(dir.create(paste0("RankList_res", ident.res, "_findAll_hgnc/"), showWarnings = FALSE))
		write.table(new.table, file = paste0("RankList_res", ident.res, "_findAll_hgnc/res", ident.res, "_cluster", cluster, ".rnk"), quote = FALSE, row.names = FALSE, col.names = TRUE, sep = "\t", )
	}
}
```

## topGO with FindAllMarkers
```{r}
source("/Users/heustonef/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/GoEnrichmentAnalysis.R")
GO_enrichment_function(my_folder = "RankList_res.0.5_findAll_hgnc/", file.pattern = ".rnk", id.type = "symbol")
```

>>>>

```{r}
for (meta.col in colnames(seurat.object@meta.data)){
	if(grepl(pattern = "RNA_snn_res", x = meta.col)==TRUE | grepl(pattern = "orig.ident", x = meta.col)==TRUE){
		myplot <- DimPlot(seurat.object, 
											group.by = meta.col,
											reduction = "umap", 
											pt.size = 1, 
											cols = color.palette) + 
			NoLegend() + 
			ggtitle(paste0(projectName, " dim", ndims, "res.", gsub("RNA_snn_res.", "", meta.col) ))
		plot(myplot)
		png(filename = paste0(projectName, " dim", ndims, "res.", gsub("RNA_snn_res.", "", meta.col), "-umap.png"), height = 800, width = 800, bg = "transparent")
		plot(myplot)
		dev.off()
		myplot <- DimPlot(seurat.object, 
											group.by = meta.col,
											reduction = "umap", 
											pt.size = 1,
											cols = color.palette) + 
			facet_wrap(meta.col) + 
			ggtitle(paste0(projectName, "dim", ndims, "res.", gsub("RNA_snn_res.", "", meta.col)))

		png(filename = paste0(projectName, "dim", ndims, "res.", gsub("RNA_snn_res.", "", meta.col), "-umap_FacetRes.png"), height = 800, width = 800, bg = "transparent")
		plot(myplot)
		dev.off()

	}
}
```
Plot all black cells
```{r}
png(filename = paste0(projectName, " dim", ndims, "-umap.png"), height = 800, width = 800, bg = "transparent")
DimPlot(seurat.object, cols = c("black", "black", "black", "black"), group.by = "orig.ident") + NoLegend()
dev.off()
```

Plot gene expression
```{r}
feature.list <- c("Meis1", "Gata2", "Gata1", "Irf8", "Elane", "Fli1", "Zfpm1")

@@

## DGE w/ resolution = 0.5
Strt with comparing all clusters against all other clusters and write out cluster info
calculate `FindAllMarkers()` for different idents and save to new file
```{r}
# ident.list <- colnames(seurat.object@meta.data)[grepl("^RNA_snn", colnames(seurat.object@meta.data))]
# ident.list <- c("RNA_snn_res.0.5", "RNA_snn_res.1")
# ident.list <- c("RNA_snn_res.1")
ident.list <- c("RNA_snn_res.0.5")
cut_off <- 1.2
load(file = "/Users/heustonef/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/mouseIDTable.rda")

@@

	## Map HGNC symbols

	HGNC <- with(mouseIDTable, mouseIDTable$HGNC[match(all.markers$gene, mouseIDTable$MGI)])
	all.markers$HGNC <- HGNC
	sig.res <- all.markers[all.markers$p_val_adj <= 0.05, ]
	sig.res <- sig.res[c("avg_log2FC", "HGNC", "cluster")]
	sig.res <- sig.res[!(sig.res$HGNC == "" | is.na(sig.res$HGNC)),] # GSEA will fail if there are any blanks or NAs in the table
	sig.res <- sig.res[]

	for(cluster in unique(sig.res$cluster)){
		print(paste("writing cluster", cluster))
		new.table <- sig.res[sig.res$cluster == cluster, c("HGNC", "avg_log2FC")]
		new.table <- new.table[order(-new.table$avg_log2FC), ]
		try(dir.create(paste0("RankList_res", ident.res, "_findAll_hgnc/"), showWarnings = FALSE))
		write.table(new.table, file = paste0("RankList_res", ident.res, "_findAll_hgnc/res", ident.res, "_cluster", cluster, ".rnk"), quote = FALSE, row.names = FALSE, col.names = TRUE, sep = "\t", )
		write.table(new.table[new.table$avg_log2FC >= cut_off,], file = paste0("RankList_res", ident.res, "_findAll_hgnc/res", ident.res, "_cluster", cluster, "-co", cut_off, "up.rnk"), quote = FALSE, row.names = FALSE, col.names = TRUE, sep = "\t", )
		write.table(new.table[new.table$avg_log2FC >= (cut_off)*-1,], file = paste0("RankList_res", ident.res, "_findAll_hgnc/res", ident.res, "_cluster", cluster, "-co", cut_off, "dn.rnk"), quote = FALSE, row.names = FALSE, col.names = TRUE, sep = "\t", )
	}
}
```

## topGO with FindAllMarkers
```{r}
source("/Users/heustonef/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/GoEnrichmentAnalysis.R")
GO_enrichment_function(my_folder = "RankList_res.0.5_findAll_hgnc/", file.pattern = ".rnk", id.type = "symbol")
# GO_enrichment_function(my_folder = "RankList_res.1_findAll_hgnc/", file.pattern = ".rnk", id.type = "symbol")
```
